---
title: "Week 1 Exercises"
author: "Jeroen Knoester"
output: pdf_document
---
# Exercise 1 - Variables
a) Write an expression to compute the sum of the numbers 3 and 4

```{r}
sum(3, 4)
```
b) Write an expression to determine if the product of 4 and 5 is equal to 21
```{r}
prod(4, 5) == 21
```
c) Create the variables *x*,*y*,*z* with values (respectively) 2, 3.5, 7
```{r}
x <- 2
y <- 3.5
z <- 7
```
d) Exploit a function of *R* to investigate the datatypeof the three variables *x*,*y*,*z*
```{r}
typeof(x)
typeof(y)
typeof(z)
```
e) Write an expression to compute the multiplication of the three variables *x*,*y*,*z*
```{r}
prod(x,y,z)
```
f) Write a Boolean expression (i.e., which result is T or F) which checks if the product of *x*,*y*,*z*  is equal to 49
```{r}
prod(x,y,z) == 49
```
g) Create a variable *s* with value "Alexander"
```{r}
s <- "Alexander"
```
h) Look for a function returning the length of a string and use it to determine the length of *s*
```{r}
nchar(s)
```  
\newpage
# Exercise 2 - Vectors
a) Create a variable ?? (a vector) with the value 1: 10
```{r}
x <- 1:10
```
b) How can you investigate the length of ???
```{r}
length(x)
```
c) Multiply *x* by the number 1.2
```{r}
x <- x*1.2
```
d) Multiply the first five elements of *x* by 2
```{r}
x[1:5] <- x[1:5] * 5
```
e) Visualize *x* using *barplot(x)*
```{r}
barplot(x)
```
f) Assign to *x* the values of all integers from 0 to 10
```{r}
x <- 1:10
```
g) Create a graph of *x* against *x* using *plot(x,x,type = "b")*
```{r}
plot(x,x,type= "b")
```
h) Use *plot* to draw the graph of the function *y* = 3*x* + 2 for values of *x* between 0 and 10
```{r}
plot(3*x+2)
```
i) Use *plot* to draw the graph of the function *y* = *sin(x)* for values of *x* between 0 and 2 pi
(use at least 200 points)
```{r}
points <- 1:200
plot(sin(points / (2 * pi)))
```
j) 