---
title: "Week 1 Exercises"
author: "Jeroen Knoester"
output: pdf_document
---
# Exercise 1 - Variables
a) Write an expression to compute the sum of the numbers 3 and 4

```{r}
sum(3, 4)
```
b) Write an expression to determine if the product of 4 and 5 is equal to 21
```{r}
prod(4, 5) == 21
```
c) Create the variables *x*,*y*,*z* with values (respectively) 2, 3.5, 7
```{r}
x <- 2
y <- 3.5
z <- 7
```
d) Exploit a function of *R* to investigate the datatypeof the three variables *x*,*y*,*z*
```{r}
typeof(x)
typeof(y)
typeof(z)
```
e) Write an expression to compute the multiplication of the three variables *x*,*y*,*z*
```{r}
prod(x,y,z)
```
f) Write a Boolean expression (i.e., which result is T or F) which checks if the product of *x*,*y*,*z*  is equal to 49
```{r}
prod(x,y,z) == 49
```
g) Create a variable *s* with value "Alexander"
```{r}
s <- "Alexander"
```
h) Look for a function returning the length of a string and use it to determine the length of *s*
```{r}
nchar(s)
```  
\newpage
# Exercise 2 - Vectors

